Automatic Extraction of JavaScript Formal Semantics from ECMAScript Specifications

### 2019-08-08 icse/eval.tex
Comments in evaluation

\begin{itemize}
  \item RQ1) Does ASE correctly extract semantics?
  \item RQ2) Is endurable size of manual portion in implementation of ASE?
  \item RQ3) Does ASE deal with annual updates from small changes?
  \item RQ4) How many specification errors are detected by ASE?
\end{itemize}

>>>>

\begin{itemize}
  \item RQ1) Does ASE correctly extract semantics? \inred{ES2020 / test262 coverage - parser / semantics}
    test262 결과를 어떻게? 전체 개수 / applicable tests 개수 / succes, fail 개수
  \item RQ2) Is endurable size of manual portion in implementation of ASE? \inred{refactoring for conversion rules / get statistics of conversion rules}
    개수만 - stmt / expr / cond / ref 몇개씩? / corner cases 개수
  \item RQ3) Does ASE deal with annual updates from small changes? \inred{proposed language features / related tests in test262 / diff of conversion rules}
    각 feature name / 의미 / compile 성공률 / 결과 test
  \item RQ4) How many specification errors are detected by ASE? \inred{supprot "Assert: ... "?/ confirm found spec errors by TC39}
\end{itemize}
